Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
Wording

We present a step-by-step refinement of a single file {\tt Fib.hs}
that contains both implementation and specs.  Each line of code is
only given once when introduced, subsequent code fragments are
incremental updates.  The reader is asked to substitute code parts as
appropriate.

@@

\noindent This concludes our example coding session.  We have seen how
to utilize behavior driven development to incrementally build a small
library.  We always extend or adapt the specification and watch it
fail first.  Then, we fix the implementation.  The combinators {\tt
shouldBe}, {\tt shouldReturn} and {\tt shouldThrow} can be used to
specify behavior of functions in an intuitive, easy to read manner.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Reusable spec}

>>>>

We present a step-by-step refinement of a library
that contains both implementation and specs.  Each line of code is
only given once when introduced, subsequent code fragments are
incremental updates.  The reader is asked to substitute code parts as
appropriate.

@@

\noindent This concludes our example coding session.  We have seen how
to utilize behavior driven development to incrementally build a small
library.  We always extend or adapt the specification first, watch it
fail,  and then fix the implementation.  The combinators {\tt
shouldBe}, {\tt shouldReturn} and {\tt shouldThrow} can be used to
specify behavior of functions in an intuitive, easy to read manner.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Reusable pieces of specification}
